---
title: "cossonet"
author: "Jieun Shin"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The component selection and smoothing operator (COSSO) is a function that estimates sparse nonlinear components. This model is an extension of the COSSO regression model to make it functional and practical for high-dimensional data. This model supports a variety of response types, including the exponential family and Cox proportional hazards models.}
  %\VignetteEngine{knitr::rmarkdown}
---

## Introduction

The package \pkg{cossonet} is an integrated function that estimates sparse nonlinear components using the COSSO penalty. This package is available from the Comprehensive R Archive Network. This script describes a example of how to use the \pkg{cossonet} package.

## Installation

We first load the library for \pkg{cossonet} and set a seed for reproducibility.

```{r, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
devtools::install_github("jiieunshin/cossonet")
library(cossonet)
set.seed(20250101)
```

## Data generation

The function \texttt{data_generation} generates example datasets with continuous response. We generate a training set with $n=200$ and $p=20$, and a test set with $n=1000$ and $p=20$.
```{r, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
tr = data_generation(n = 200, p = 20, SNR = 9, response = "continuous")
te = data_generation(n = 1000, p = 20, SNR = 9, response = "continuous")
```

## Model fitting

The function \texttt{cossonet} is the main function that fits the model. We have to input training set in this function. And Specific values are required to the arguments, such as  \texttt{family}, \texttt{lambda0}, and \texttt{lambda_theta}.

```{r, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
lambda0_seq = exp(seq(log(2^{-5}), log(2^{-1}), length.out = 20))
lambda_theta_seq = exp(seq(log(2^{-8}), log(2^{-5}), length.out = 20))

fit = cossonet(tr$x, tr$y, family = 'gaussian',
	       lambda0 = lambda0_seq,
	       lambda_theta = lambda_theta_seq
	       )
```

## Prediction

The function \texttt{cossonet.predict} is used to predict new data based on the fitted model. The output includes predicted values $\hat{f}$ (from \texttt{f.new}) and $\hat{\mu}$ (from \texttt{mu.new}) for the new data. The predicted value and predictive accuracy for the test set using our fitted model can be obtained by
```{r, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
pred = cossonet.predict(fit, te$x)
mean((te$f - pred$f.new)^2)
```
